Blocking-resistant communication through high-value web services

### 2014-05-12 docs/meek.tex
Start a list of acknowledgements.
Start an abstract.

\setlength{\parskip}{\baselineskip}

@@

@@

>>>>

@@

\maketitle

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
A key technique we use is ``domain fronting''---communicating with
a forbidden domain name while appearing to communicate with one that is allowed.
\end{abstract}

@@

\section{Acknowledgements}

tor-dev
tor-qa
George Kadianakis
Georg Koppen
Lunar
Yawning Angel
Vern Paxson
Nick Weaver
